---
title: "TD3_v2"
author: "Etanlink and Thomas Debuger"
date: "January 2017"
output:
  html_document: default
  pdf_document:
    number_sections: yes
subtitle: Statistical Analysis of Ping-Pong
geometry: margin=1.5in, top=0.5in, bottom=0.5in
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction


# Real Ping-Pong Measurements

```{r}
pp1 <- read.csv("data/PP_size_1.csv");
head(pp1);
```

## Plots of real ping-pong measurements

### Plot 2
```{r, fig.width=6, fig.height=3.5}
plot(pp1$time*1000, ylab="Time (milliseconds)", xlab="Measurement Number");
```
C'est régulier dans le temps. (Etude partie basse, étude partie haute)
 
## Statistical Summary

A summary of a set of values can be easily obtained in R with (`df$time` is a vector with the measurements -- it represents the column `time` of the data frame `df`). So, calling the function `summary` on this vector gives:

```{r pp1}
summary(pp1$time*1000);
```

## Boxplot

```{r, fig.width=2, fig.height=3.5}
boxplot(pp1$time*1000, ylab="Time (milliseconds)")
```

## Histogram

```{r pp1, fig.width=3}
hist(pp1$time*1000, breaks=7, xlab="Time (milliseconds)", main="Histogram of Ping-Pong")
```

## Variability

As we previously mentioned, ping-pong measurements suffer external influences that might affect estimations. As a consequence, we need to evaluate the variability. A common measure of variability is the standard deviation, calculated like this:
```{r}
sd(pp1$time*1000)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
